Biomass trend maps

### 2019-06-21 analysis/VOCC/biomass-trends.Rmd
new covariates ready for the prediction grid; false start on integrating them with fishing_event data...

if (!exists("nd_all")) {
  bath <- readRDS("data/bathymetry-data")

  # choose base year(s) to create grid from
  dummy_year <- c(2005, 2006)
  dat <- bath$data %>% scale_survey_predictors()

@@

Run sdmTMB model (if not done previously).
```{r eval=FALSE}
if (update_spatial_model) {
  biomass <- readRDS(paste0("data/", spp, "/data-by-maturity-", spp, "-", ssid_string, ".rds"))
  data <- biomass %>% gfranges:::scale_survey_predictors()

>>>>

if (!exists("nd_all")) {

  # choose base year(s) to create grid from
  dummy_year <- c(2005, 2006)

  # bath <- readRDS("data/bathymetry-data")
  # dat <- bath$data %>% scale_survey_predictors()

  newcov <- readRDS("data/new_covariates.rds")
  dat <- newcov %>% gfranges::scale_survey_predictors()

@@

Run sdmTMB model (if not done previously).
```{r eval=FALSE}
if (update_spatial_model) {
  biomass <- readRDS(paste0("data/", spp, "/data-by-maturity-", spp, "-", ssid_string, ".rds"))
  covars <- readRDS("event-covariates.rds")
  data <- left_join(biomass, covars)

  data <- data %>% gfranges:::scale_survey_predictors()
